DOpElib:\\ Differential Equations and Optimization Environment

### 2017-05-17 Examples/Documentation/introduction.tex

This means that the Makefile in the specific examples folder has been 
modified in some illegal way. Remove this Makefile 
\begin{lstlisting}
rm Makefile
rm -r CMakeFiles
rm CMakeCache.txt
rm -r autobuild
\end{lstlisting}
and get the original 
one from DOpElib:
\begin{lstlisting}
git checkout Makefile
\end{lstlisting}
Then try again make c-all (make always sure that before 
typing make c-all that the deal.II path is exported - see above).
\newline
\subsection*{4.) Different g++ compilers are used for compiling DOpElib and the
Examples folder}

\begin{lstlisting}
bernhard@ebook:~/Schreibtisch/Prog/DOpe/Dope/dopelib/Examples> make c-all
cd OPT/StatPDE/Example1; make -s c-all
[ 50%] Building CXX object CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o
c++: error: unrecognized command line option '-fopenmp-simd'
c++: error: unrecognized command line option '-std=c++14'
CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/build.make:62: recipe for target
'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o' failed
make[4]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o] Error 1
CMakeFiles/Makefile2:131: recipe for target
'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all' failed
make[3]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all] Error 2
Makefile:83: recipe for target 'all' failed
make[2]: *** [all] Error 2
../../../..//Examples/Make.global_options:2: recipe for target 'c-all' failed
make[1]: *** [c-all] Error 2
Makefile:24: recipe for target 'OPT/StatPDE/Example1' failed
make: *** [OPT/StatPDE/Example1] Error 2
\end{lstlisting}
The reason for this problem might be that the variables c++ and g++ as well as
cc and gcc do not match.
You can remove the old Examples folder and replace it by a new one and set the
compilers manually by
\begin{lstlisting}
export CXX=path/to/g++-compiler
export CC=path/to/gcc-compiler
\end{lstlisting}
where path/to/compiler should be the path to compiler DOpElib was compiled with.
You can check the current version of your gcc- and g++-compiler with
\begin{lstlisting}
gcc --version
g++ --version
\end{lstlisting}
Alternatively you can set the variable c++ to your g++ and the variable cc to
gcc using update-alternatives
as for example
\begin{lstlisting}
sudo update-alternatives --install /usr/bin/c++ c++ /usr/bin/g++-6 60
sudo update-alternatives --install /usr/bin/cc cc /usr/bin/gcc-6 60
\end{lstlisting}
Thanks to Florian Tischler (Admin at RICAM Linz) for the help.

>>>>

This means that the Makefile in the specific examples folder has been 
modified in some illegal way. Remove this Makefile 
\begin{lstlisting}
rm Makefile
rm -r CMakeFiles
rm CMakeCache.txt
rm -r autobuild
\end{lstlisting}
and get the original 
one from DOpElib:
\begin{lstlisting}
git checkout Makefile
\end{lstlisting}
Then try again make c-all (make always sure that before 
typing make c-all that the deal.II path is exported - see above).

\subsection*{4.) Different g++ compilers are used for compiling DOpElib and the Examples folder}
\begin{lstlisting}
bernhard@ebook:~/Schreibtisch/Prog/DOpe/Dope/dopelib/Examples> make c-all
cd OPT/StatPDE/Example1; make -s c-all
[ 50%] Building CXX object CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o
c++: error: unrecognized command line option '-fopenmp-simd'
c++: error: unrecognized command line option '-std=c++14'
CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/build.make:62: recipe for target 'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o' failed
make[4]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/main.cc.o] Error 1
CMakeFiles/Makefile2:131: recipe for target 'CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all' failed
make[3]: *** [CMakeFiles/DOpE-OPT-StatPDE-Example1.dir/all] Error 2
Makefile:83: recipe for target 'all' failed
make[2]: *** [all] Error 2
../../../..//Examples/Make.global_options:2: recipe for target 'c-all' failed
make[1]: *** [c-all] Error 2
Makefile:24: recipe for target 'OPT/StatPDE/Example1' failed
make: *** [OPT/StatPDE/Example1] Error 2
\end{lstlisting}

The reason for this problem might be that the variables c++ and g++ as well as cc and gcc do not match.
\newline
You can remove the old Examples folder and replace it by a new one and set the compilers manually by
\begin{lstlisting}
export CXX=path/to/g++-compiler
export CC=path/to/gcc-compiler
\end{lstlisting}
where path/to/compiler should be the path to compiler DOpElib was compiled with.
You can check the current version of your gcc- and g++-compiler with 
\begin{lstlisting}
gcc --version
g++ --version
\end{lstlisting}
Alternatively you can set the variable c++ to your g++ and the variable cc to gcc using update-alternatives
as for example
\begin{lstlisting}
sudo update-alternatives --install /usr/bin/c++ c++ /usr/bin/g++-6 60
sudo update-alternatives --install /usr/bin/cc cc /usr/bin/gcc-6 60
\end{lstlisting}
Thanks to Florian Tischler (Admin at RICAM Linz) for the help.
